Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
Minor changes

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
source (stars, MSPs, SNe Ia, and black hole feedback).  MSP heating is
again found to be negligible at all black hole masses.  The young
stellar populations in galaxies with $\Mbh\lsim 10^{7.5} \Msun$
results in $v_{w}^{\star}$ being dominant.  For $\Mbh\gsim 10^{7.5}
\Msun$, the lack of younger stellar populations reduces the role of
stellar wind heating, but Compton heating plays an important role.

@@

Figure~\ref{fig:cooling2} shows the ratio of heating to radiative
cooling at the stagnation radius (eq.~[\ref{eq:cooling2}]) as a
function of SMBH mass, using our total heating rate from Figure
\ref{fig:vWsources}.  The combined heating rate from stellar winds and
Compton heating is insufficient to prevent thermal instability for the
high $\Mbh$.  However, if Ia supernovae are included in the schematic
way described above, the flow again becomes thermally stable for $\Mbh
\gtrsim XXXX$.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{\rm edd}$ predicted
  from our models compared to $L_X/L_{\rm edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
  Appendix~\ref{app:windheat} for a detailed description).
  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}

>>>>

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
source (stars, MSPs, SNe Ia, and black hole feedback).  MSP heating is
again found to be negligible at all black hole masses.  The young
stellar populations in galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$
results in $v_{w}^{\star}$ being dominant.  For $\Mbh\gsim 5\times 10^{8}
\Msun$, the lack of younger stellar populations reduces the role of
stellar wind heating, but Compton heating plays an important role.

@@

The bottom panel of Figure~\ref{fig:vwSources} shows the ratio of
heating to radiative cooling at the stagnation radius
(eq.~[\ref{eq:cooling2}]) as a function of SMBH mass, using our total
heating rate from the top panel Figure \ref{fig:vwSources}.  The
combined heating rate from stellar winds and Compton heating is
insufficient to prevent thermal instability for the high $\Mbh$.
{\bf AG: Should we really be talking about Compton heating stabilizing
the flow}?
% However, if Ia supernovae are included in the schematic way described
% above, the flow again becomes thermally stable for $\Mbh \gtrsim
% XXXX$.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{\rm edd}$ predicted
  from our models compared to $L_X/L_{\rm edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources} and~\ref{fig:eta}--see
  Appendix~\ref{app:windheat} for a detailed description).
  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}
